---
title: "Plant Histogram Presentation"
author: "Dev Das"
date: "November 25, 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Agenda
This presentation will focus on the following  

- Plant Summary Data
- Plant Plot
- Some Conclusions

## Summary of Plant Growth Dataset

The plant growth dataset is separated into two columns. The first is a column of plant weights, while the second is the group that the plants are assigned to. The summary of the data below, shows the plant weights have a range of 2.72
```{r cars, echo = TRUE}
summary(PlantGrowth)
```

## Plot of Plant Weights

The histogram of plant weights is below, with a median of 5.155

```{r pressure}
x    <- PlantGrowth$weight


hist(x, col = "#228B22", border = "yellow",
     xlab = "Plant Weight",
     main = "Histogram of Plant Weights")
```

## Conclusions

We can conclude from our small summary data and plot, that the plant data is skewed to the left, with some plants being under 4 inches. The data is centered around the median of 5.155, with a max of 6.31 and a min of 3.59. With more data points the distribution could turn normal with the help of the central limit theorem